### 2016-05-07 sec1_introduction_bk.tex
Some modifications
Need revise sec 1 and 3

\begin{table} \scriptsize
\centering
\begin{tabular}{|c|c|c|c|}
\hline 
 & Spatial Proximity & Consecutiveness &  Time Complexity\\ 
\hline 
flock~\cite{gudmundsson2004flock} & disk-based &  global & $O(|\mathbb{O}||T|^2 + |\mathbb{O}|log(|\mathbb{O}|))$ \\ 
\hline 
convoy~\cite{jeung2008convoy} & density-based &   global & $O(|T|^2+|\mathbb{O}||T|)$\\ 
\hline 
group~\cite{wang2006grouppattern} & disk-based &  local & $O(|\mathbb{O}|^2|T|)$ \\ 
\hline 
swarm~\cite{li2010swarm} & density-based  & no constraint & $O(2^{|\mathbb{O}|}|\mathbb{O}||T|)$  \\ 
\hline 
platoon~\cite{li2015platoon} & density-based &  local & $O(2^{|\mathbb{O}|}|\mathbb{O}||T|)$\\ 
\hline 
\end{tabular} 
\caption{Existing co-movement patterns. The time complexity stated are based on worst case analysis, where $|\mathbb{O}|$ is the size of object, $|T|$ is the maximum size of timestamps among all trajectories.}
\label{tbl:existing_co_patterns}
\end{table}

@@

As can be seen, there are various co-movement patterns requested by different applications and it is cumbersome to design a tailored solution for each type. Hence, there is a particular demand for a general platform to support all these co-movement patterns. The other issue with existing methods is that they are built on top of centralized indexes that are not scalable. To the best of our knowledge, the maximum number of trajectories ever evaluated is up to hundreds of thousands of trajectories. In practice, it is rather common to collect at least millions of trajectories and their scalability is left unknown. We, for the first time, evaluate the pattern mining performance at the million scale and report the performance in Figure~\ref{}. The results show that their performance degrades dramatically as the dataset size scales up. In fact, as shown in Table~\ref{tbl:existing_co_patterns}, the mining of co-movement patterns require high complexity. For instance, the
complexities of \emph{swarm} and \emph{platoon} are already exponential. 
Therefore, none of them can handle millions of trajectories efficiently. 
%CAN YOU ANALYSE THEIR COMPLEXITY TO ADDRESS THE PROBLEM OF SCALABILITY.

@@

Second, we propose a parallel solution based on modern MapReduce platform for scalable pattern mining. Our
solution is a three-step MapReduce alike approach. First, trajectories are partitioned
into snapshots where clusters from each snapshots are formed in parallel. Second, 
clusters at various timestamps are shuffled and regrouped. Third, the general co-movement patterns
are mined from each group. The challenge here is to ensure that
the patterns mined at step three is complete. If not, further shuffles and computations are required which 
significantly drag down the system performance. In order to resolve the challenges and meanwhile keep the 
shuffle amount at each stage to a minimum, 
we design a novel star-based partition scheme to efficiently partition objects based on their
belonging clusters. Based on the star partition, we then propose a series of optimization techniques which
largely improve the system performance. NEED TO EMPHASIZE YOUR TECHNICAL CONTRIBUTION!

>>>>

\begin{table} \scriptsize
\centering
\begin{tabular}{|c|c|c|c|}
\hline 
 & Spatial Proximity & Consecutiveness &  Time Complexity\\ 
\hline 
flock~\cite{gudmundsson2004flock} & disk-based &  global & $O(|\mathbb{O}||\mathbb{T}|^2 + |\mathbb{O}|log(|\mathbb{O}|))$ \\ 
\hline 
convoy~\cite{jeung2008convoy} & density-based &   global & $O(|T|^2+|\mathbb{O}||\mathbb{T}|)$\\ 
\hline 
group~\cite{wang2006grouppattern} & disk-based &  local & $O(|\mathbb{O}|^2|\mathbb{T}|)$ \\ 
\hline 
swarm~\cite{li2010swarm} & density-based  & no constraint & $O(2^{|\mathbb{O}|}|\mathbb{O}||\mathbb{T}|)$  \\ 
\hline 
platoon~\cite{li2015platoon} & density-based &  local & $O(2^{|\mathbb{O}|}|\mathbb{O}||\mathbb{T}|)$\\ 
\hline 
\end{tabular} 
\caption{Existing co-movement patterns. The time complexity stated are based on worst case analysis, where $|\mathbb{O}|$ is the total number of objects, $|\mathbb{T}|$ is the total number of timestamps.}
\label{tbl:existing_co_patterns}
\end{table}

@@

As can be seen, there are various co-movement patterns requested by different applications and it is cumbersome to design a tailored solution for each type. Hence, there is a particular demand for a general platform to support all these co-movement patterns. The other issue with existing methods is that they are built on top of centralized indexes that are not scalable. To the best of our knowledge, the maximum number of trajectories ever evaluated is up to hundreds of thousands of trajectories. In practice, it is rather common to collect at least millions of trajectories and their scalability is left unknown. We, for the first time, evaluate the pattern mining performance at the million scale and report the performance in Figure~\ref{}. The results show that their performances degrade dramatically as the dataset size scales up. In fact, as shown in Table~\ref{tbl:existing_co_patterns}, the mining of co-movement patterns require high complexity. For instance, the
complexities of \emph{swarm} and \emph{platoon} are already exponential. 
Therefore, none of them can handle millions of trajectories efficiently. 
%CAN YOU ANALYSE THEIR COMPLEXITY TO ADDRESS THE PROBLEM OF SCALABILITY.

@@

Second, we propose a parallel solution on modern MapReduce platforms for scalable pattern mining.
The major challenge in designing MapReduce-based algorithms is to make proper partitions of input data.
In GCMP mining, we enforce both the \emph{soundness} and the \emph{completeness} 
of the partitions. Such properties ensure that neither false-patterns 
nor miss-patterns are possible in our solution. To meet such partition requirements
as well as to keep the shuffle amount to a minimum,
% 
%%Second, we propose a . Our
%%solution is a three-step MapReduce alike approach. First, trajectories are partitioned
%%into snapshots where clusters from each snapshots are formed in parallel. Second, 
%%clusters at various timestamps are shuffled and regrouped. Third, the general co-movement patterns
%%are mined from each group. 
%
%The challenge here is to ensure that
%the patterns mined at step three is complete. If not, further shuffles and computations are required which 
%significantly drag down the system performance. In order to resolve the challenges and meanwhile keep the 
%shuffle amount at each stage to a minimum, 
we first design a naive \emph{Temporal Replication and Mining} (TRM)
approach, which partitions trajectories into groups of consecutive snapshots. Then, we design a line-sweep
method for mining GCMP from each partition. We prove that in TRM, the partition is complete and sound when a snapshot is replicated $O(|T|)$ times. 
Then, we design a novel \emph{Star Partition and Mining} (SRM) approach which significantly reduces the data shuffled
as compare to TRM. In SRM, we design a conceptual connection graph based on proximity among objects. We adapt
a \emph{star partition} which cut the graph by replicating vertices. Afterwards, we design an Apriori-like method to mine
GCMP in each partition. We prove the correctness of SPM and show that total data been replicated is $O(|\mathbb{O}|)$.
Moreover, we utilize \emph{temporal monotonicity} in GCMP to further reduce the shuffling and mining cost in SPM. Lastly, we adapt various engineering level techniques to support efficiently deploying our algorithms in 
Apache Spark which is one of the most popular MapReduce platforms.

%we design a novel star-based partition scheme to efficiently partition objects based on their
%belonging clusters. Based on the star partition, we then propose a series of optimization techniques which
%largely improve the system performance. NEED TO EMPHASIZE YOUR TECHNICAL CONTRIBUTION!

### 2016-05-07 sec3_definitions.tex
Some modifications
Need revise sec 1 and 3

To control the closeness of timestamps, we further define the $G$-connected of a time sequence as follows: WHAT THE RELATIONSHIP BETWEEN CLOSENESS AND G-CONNECTED?

%
%
%We say a sequence $T$ is \emph{(fully)consecutive}
%if and only if $\forall T[i] \in T, T[i+1] \in T$, $T[i+1] = T[i] + 1$. A subsequence $T^m$ is \emph{maximally consecutive}~\cite{li2015platoon} wrt. $T$ if and only if $T^m \subseteq T$ and $\nexists T^{m'}, T^m \subseteq T^{m'} \wedge T^{m'} $ is consecutive. For example, let $T=\{1,2,3,5,6\}$, then $T_1=\{1,2,3\}$ and $T_2=\{5,6\}$ are two maximally consecutive subsequences wrt. $T$. We then define the $L$-consecutiveness as follows:

@@

\begin{definition}[$G$-connected]
A time sequence $T$ is $G$-connected if the gap between any of its neighboring timestamps is no greater than $G$. That is
 $\forall T[i],T[i+1] \in T, T[i+1]-T[i] \leq G$.
\end{definition}

We take $T=\{1,2,3,5,6\}$ as an example, which can be decomposed into two consecutive segments $\{1,2,3\}$ and $\{5,6\}$. $T$ is not $3$-consecutive since the length $\{5,6\}$ is $2$. Thus, it is safe to say either $T$ is $1$-consecutive or $2$-consecutive. On the other hand, $T$ is $2$-connected since the maximum gap between its neighboring time stamps is $5-3=2$. It is worth noting that $T$ is not $1$-connected because XXX.

@@

%\begin{enumerate}
%\item{Closeness: $\forall o_i,o_j \in O, \forall t \in T, C_t(o_i) = C_t(o_j)$}
%\item{Significance: $|O| \geq M$}
%\item{Duration: $|T| \geq K$}
%\item{Consecutiveness: $T$ is $L$-consecutive}
%\item{Separateness: $T$ is $G$-separated}
%\end{enumerate} 
\end{definition}
There are XXX parameters in our general co-movement pattern, including XXX. By customizing these parameters, our pattern can be reduced to the patterns proposed in previous literature, as illustrated in Table~\ref{tbl:patterns}. In particular, by setting $G=|T|$, we achieve the \emph{platoon} pattern. By setting $G=|T|,L=1$, we achieve the \emph{swarm} pattern. By setting $G=|T|$, $M=2$, $K=1$, we gain the \emph{group} pattern. Finally by setting $G=1$, we achieve the \emph{convoy} and \emph{flock} pattern. 
In addition to covering existing patterns, the general co-movement pattern avoids the \emph{loose connection} problem in \emph{platoon} pattern. As suggested previously, $\{1,2, 100,101\}$ will be included in the platoon pattern, however since they're too far away, this pattern is not prominent. By setting appropriate $G$, we are able to prune this anomaly. It is notable that GCMP is not able to be modeled by existing patterns. AS MENTIONED IN WECHAT, POLISH THIS PART.

%The general co-movement pattern retains the patterns that discovered by all 
%existing techniques (group, flock, convoy, swarm and platoon). 
%The relationships between general co-movement pattern and other patterns are summarized 
\begin{table}
\centering
\begin{tabular}{|c|c|c|c|c|}
\hline 
Pattern & $L$ & $G$ & $M$ & $K$ \\ 
\hline
Group & $\cdot$ & $|T|$ & $2$ & $1$ \\
\hline
Flock & $K$ & 1 & $\cdot$ & $\cdot$ \\
\hline 
Convoy & $K$ & $1$ & $\cdot$ & $\cdot$\\ 
\hline 
Swarm & $1$ & $|T|$ & $\cdot$ & $\cdot$ \\ 
\hline 
Platoon & $\cdot$ & $|T|$ & $\cdot$ & $\cdot$\\ 
\hline 
\end{tabular} 
\caption{Representing other patterns using GCMP. $\cdot$ means user specified value.}
\label{tbl:patterns}
\end{table}

It is also observable that the number of patterns in GCMP is exponential. To control the size of output, 
we notice that, for two patterns $P_1,P_2$, if $P_1.O \subseteq P_2.O$ and $P_2$ is a proper pattern, then $P_1$ is also a proper pattern. Therefore, we can define the \emph{Closed General Co-Movement Pattern} as follows:

\begin{definition}[Closed General Co-Movement Pattern]
A general co-moving pattern $P=\langle O, T \rangle$ is closed if and only if there does not exist another general co-moving pattern $P'$ s.t. $P.O \subseteq P'.O$.
\end{definition}

For example, let $n=2,k=2,l=1,g=1$, the pattern $\{o_1,o_2\}\{1,2,3,4\}$ is not a closed pattern, while $\{o_1,o_2,o_3\}$ $\{1,2,3,4\}$ is a closed pattern. The closed pattern avoids outputting duplicate information, thus making the result patterns more compact.

@@

%Although the general co-moving pattern is free from the clustering methods used at each snapshot, as suggested in~\cite{jeung2008convoy}, the \emph{density}-based clustering method is better in detecting object clusters with arbitrary spatio-shapes. Therefore in this paper, we mainly consider density-based clustering.
Our definition of GCMP is free from clustering method. Users are able to supply different clustering method to facilitate different needs. We currently expose both disk-region based clustering and DBSCAN as options to the user.

@@

\begin{table}[h]
\centering
\begin{tabular}{|c|c|} 
\hline
Symbols & Meanings \\
\hline 
$Tr_i$ & Trajectory of object $i$\\ 
\hline
$S_t$ & Snapshot of objects at time $t$ \\
\hline 
$\mathbb{O}$ & Set of objects \\ 
\hline 
$T$ & Time sequence \\
\hline
$C_t(o)$ & the cluster of object $o$ at time $t$ \\
\hline 
$Sr_i $ &  The star structure of object $i$ \\
\hline 
\end{tabular} 
\caption{Notions that will be used}
\end{table}

>>>>

As illustrate in Figure~\ref{fig:platoon_weakpoint}, patterns adapting the notion of $L$-consecutiveness (e.g., \emph{platoon} and \emph{group}) still suffer from \emph{loose connection} problem. 
To avoid such an anomaly without losing pattern generality, we introduce a parameter $G$ to control the gaps between
timestamps in a pattern. Formally, a $G$-connected time sequence is defined as follows:
%To control the closeness of timestamps, we further define the $G$-connected of a time sequence as follows: WHAT THE RELATIONSHIP BETWEEN CLOSENESS AND G-CONNECTED?
%
%
%We say a sequence $T$ is \emph{(fully)consecutive}
%if and only if $\forall T[i] \in T, T[i+1] \in T$, $T[i+1] = T[i] + 1$. A subsequence $T^m$ is \emph{maximally consecutive}~\cite{li2015platoon} wrt. $T$ if and only if $T^m \subseteq T$ and $\nexists T^{m'}, T^m \subseteq T^{m'} \wedge T^{m'} $ is consecutive. For example, let $T=\{1,2,3,5,6\}$, then $T_1=\{1,2,3\}$ and $T_2=\{5,6\}$ are two maximally consecutive subsequences wrt. $T$. We then define the $L$-consecutiveness as follows:

@@

\begin{definition}[$G$-connected]
A time sequence $T$ is $G$-connected if the gap between any of its neighboring timestamps is no greater than $G$. That is
 $\forall T_i,T_{i+1} \in T, T_{i+1}-T_{i} \leq G$.
\end{definition}

We take $T=\{1,2,3,5,6\}$ as an example, which can be decomposed into two consecutive segments $\{1,2,3\}$ and $\{5,6\}$. $T$ is not $3$-consecutive since the length $\{5,6\}$ is $2$. Thus, it is safe to say either $T$ is $1$-consecutive or $2$-consecutive. On the other hand, $T$ is $2$-connected since the maximum gap between its neighboring time stamps is $5-3=2$. It is worth noting that $T$ is not $1$-connected because the gap between $T_3$ and $T_4$ is 2 (i.e., 5-3=2).

@@

%\begin{enumerate}
%\item{Closeness: $\forall o_i,o_j \in O, \forall t \in T, C_t(o_i) = C_t(o_j)$}
%\item{Significance: $|O| \geq M$}
%\item{Duration: $|T| \geq K$}
%\item{Consecutiveness: $T$ is $L$-consecutive}
%\item{Separateness: $T$ is $G$-separated}
%\end{enumerate} 
\end{definition}
There are four parameters in our general co-movement pattern, including object constraint $M$ and temporal constraints $K,L,G$. By customizing these parameters, our pattern can 
express other patterns proposed in previous literature, as illustrated in Table~\ref{tbl:patterns}. 
In particular, by setting $G=|T|$, we achieve the \emph{platoon} pattern. By setting $G=|T|,L=1$, we achieve the \emph{swarm} pattern. By setting $G=|T|$, $M=2$, $K=1$, we gain the \emph{group} pattern. Finally by setting $G=1$, we achieve the \emph{convoy} and \emph{flock} pattern. 
In addition to the flexibility of representing other existing patterns, our GCMP is able to avoid the \emph{loose connection} anomaly by tuning the parameter $G$. 
%In addition to covering existing patterns, the general co-movement pattern avoids the \emph{loose connection} problem in \emph{platoon} pattern. 
%
%As suggested previously, $\{1,2, 100,101\}$ will be included in the platoon pattern, however since they're too far away, this pattern is not prominent. By setting appropriate $G$, we are able to prune this anomaly. 
It is notable that GCMP cannot be modeled by existing patterns. AS MENTIONED IN WECHAT, POLISH THIS PART.

%The general co-movement pattern retains the patterns that discovered by all 
%existing techniques (group, flock, convoy, swarm and platoon). 
%The relationships between general co-movement pattern and other patterns are summarized 
\begin{table}
\centering
\begin{tabular}{|l|c|c|c|c|c|}
\hline 
Pattern & $M$ & $K$ & $L$ & $G$ & Clustering\\ 
\hline
Group & $2$ & $1$ & $2$ & $|T|$ & Disk-based\\
\hline
Flock & $\cdot$ & $\cdot$ & $K$ & $1$ & Disk-based \\
\hline 
Convoy & $\cdot$ & $\cdot$ & $K$ & $1$ & Density-based\\ 
\hline 
Swarm & $\cdot$ & $\cdot$ & $1$ & $|T|$ & Density-based \\ 
\hline 
Platoon & $\cdot$ & $\cdot$ & $\cdot$ & $|T|$ & Density-based\\ 
\hline 
\end{tabular} 
\caption{Expressing other patterns using GCMP. $\cdot$ indicate a user specified value. $M$ represents the 
object \emph{size} constraints. $K$ represents \emph{duration} constraint. $L$ represents \emph{consecutiveness} constraint. $G$ represents the \emph{connection} constraints.}
\label{tbl:patterns}
\end{table}

It is also observable that the number of patterns in GCMP is exponential. To reduce the size of output, 
we notice that, for two patterns $P_1,P_2$, if $P_1.O \subseteq P_2.O$ and $P_2$ is a proper pattern, then $P_1$ is also a proper pattern. Therefore, we can define the \emph{Closed General Co-Movement Pattern} as follows:

\begin{definition}[Closed General Co-Movement Pattern]
A general co-moving pattern $P=\langle O:T \rangle$ is closed if and only if there does not exist another general co-moving pattern $P'$ s.t. $P.O \subseteq P'.O$.
\end{definition}

For example, let $M=2,K=2,,L=1,G=1$. In Figure~\ref{fig:related_work},
the pattern $P_1 = \{o_3,o_4:1,2,3\}$ is not a closed pattern. This is because $P_2=\{o_3,o_4,o_5:2,3\}$ is a closed pattern and $P_2.O \supset P_1.O$. The closed pattern avoids outputting duplicate information, thus making the result patterns more compact.

@@

%Although the general co-moving pattern is free from the clustering methods used at each snapshot, as suggested in~\cite{jeung2008convoy}, the \emph{density}-based clustering method is better in detecting object clusters with arbitrary spatio-shapes. Therefore in this paper, we mainly consider density-based clustering.
Our definition of GCMP is free from clustering method. Users are able to supply different clustering methods to facilitate different application needs. 
We currently expose both disk-region based clustering and DBSCAN as options to the user.

@@

\begin{table}[h]
\centering
\begin{tabular}{|c|l|} 
\hline
Symbols & Meanings \\
\hline 
$Tr_i$ & Trajectory of object $i$\\ 
\hline
$S_t$ & Snapshot of objects at time $t$ \\
\hline 
$\mathbb{O}$ & Set of objects \\ 
\hline 
$K$ & Duration constraint\\
\hline
$M$ & Object size constraint \\
\hline
$L$ & Consecutiveness constraint\\
\hline
$G$ & Connection constraint \\
\hline
$T$ & Time sequence \\
\hline
$C_t(o)$ & the cluster of object $o$ at time $t$ \\
\hline 
$Sr_i $ &  The star structure of object $i$ \\
\hline 
\end{tabular} 
\caption{Notions that will be used}
\end{table}

### 2016-05-07 sec4_system.tex
Some modifications
Need revise sec 1 and 3

\section{Overview of Mining GCMP in Parallel}
\label{sec:system_overview}
We adapt the MapReduce paradigm for designing
a parallel solution of mining GCMP. 
MapReduce was proposed by Dean et. cl.~\cite{dean2008mapreduce}
and has become a mature parallel platform for large-scaled data processing. 
Current open source MapReduce systems provide handy programming APIs with fault tolerances
in backends. Such systems include Hadoop, Shark and Spark to name a few.

In simple words, there are two types of computing nodes in MapReduce,
namely the \emph{mapper}s and the \emph{reducer}s. The execution of a MapReduce task consists of
three stages: First, input data
are partitioned and read by a \emph{map} function on each mapper. Then, mappers
emit key-value pairs which are \emph{shuffle}d over the network to reducers. Finally,
reducers process received data using a \emph{reduce} function then write the
outputs.
Since the \emph{shuffle} stage needs to transfer data over network, 
an important attention to pay during designing MapReduce an algorithm is 
to minimize the shuffle amounts and shuffle counts.

Our GCMP mining framework consists of two MapReduce jobs which
are constituted of four MapReduce stages as illlustrated in Figure~\ref{fig:overview}.
The first MapReduce job corresponds to Figures~\ref{fig:overview}(a)-(b). The objective
of the first job is to cluster trajectories based on snapshots (i.e., computing $\forall t, o, C_t(o)$).
As illustrated in (a), input trajectories are read in by mappers 
and are sprinkled into $\langle t,o \rangle$ pairs. In (b), objects with the same timestamp
form a snapshot. Then, a user defined clustering method is applied on the objects
in each snapshot in reducers. Between step (a) and (b), a shuffle is necessary. The second
MapReduce job corresponds to Figures~\ref{fig:overview} (c)-(d). The objective 
of the second job is to mine the GCMP from the snapshots computed in the first job. We design
two approaches (to be described shortly)for mining GCMP in parallel. In overview, as shown in (c), snapshots
are first fed to mappers and different partition strategies may be selected to create
partitions among snapshots. In (d), the partitions are then send to reducers to mine GCMP.
The final computed results are then outputted to the end users. Although we need two MapReduce
jobs for a complete GCMP mining framework, we may pipeline the two jobs to exploit the data locality.
Specifically, the reducer output at step (b) can be directly reused as the input to mappers at step (c). Therefore
we do not need to transfer data from step (b) to step (c). Modern MapReduce platforms, especially Spark, have
already supported such a kind of pipeline.

\begin{figure} [t]
\center
\includegraphics[width=0.5\textwidth]{system_layout.eps}
\caption{System flow of mining GCMP}
\label{fig:overview}
\end{figure}

The first MapReduce job to compute clusters in each snapshot
is easy to work in parallel. This is because a clustering method only needs
to access data within in a snapshot. 
In contrast, it is challenging
to design a partition-and-mining methods for the second job. This is because
valid patterns may spray across multiple snapshots, where inappropraite partition
may fail to discover some valid patterns.
Formally, a reasonable partition strategy 
needs to meet the following requirements: first, the resulted partitions need
to preserve enough information so that real patterns can be discovered in the reduce phase. 
Second, the resulted partitions need to ensure that
the patterns discovered in the reduce phase are real patterns so that
no further validation is required. We formalize the two 
properties as \emph{completeness} and \emph{soundness} as follows:

\begin{definition}[Completeness and Soundness]
Let a partition method $\mathbb{P}$ partitions original trajectories $Tr$ into multiple parts, $Par_1,...,Par_m$. $\mathbb{P}$ is complete if for every pattern $P$ that is valid in $Tr$, $\exists Par_i$ such that $P$ is valid in $Par_i$. $\mathbb{P}$ is sound if for all patterns $P$ that is valid in any $Par_i$, it is also valid in $TR$.
\end{definition}
The completeness ensures that no true patterns are missed out. The soundness ensures that no false patterns are reported. 
If a partition method is both sound and complete, we are then able to design a MapReduce algorithm to facilitate the second job
of our framework.

Apparently, replicating the entire trajectories to each 
partition meets the \emph{soundness} and \emph{completeness}. However, 
it burdens the network shuffle and limits the parallelism. 
Our objective is thus to design a complete and sound partition method that minimize the network shuffles.
In the following sections, we first present a naive \emph{temporal-based} partition-and-mining method called \emph{Temporal Replication and Mining}(TRM) towards a parallel solution of GCMP mining. Then,
we further present a novel \emph{object-based} partition-and-mining method
called \emph{Star Partition and Mining} (SPM) which resolves
the deficiency of TRM method.

>>>>

\section{Overview of Mining GCMP in Parallel}
\label{sec:system_overview}
We adapt the MapReduce paradigm for designing
a parallel solution of mining GCMP. In this section,
we briefly cover the preliminary on MapReduce and then describe
the overview of our framework in mining GCMP.

\subsection{Preliminary on MapReduce}
MapReduce (MR) was formally proposed by Dean et. al.~\cite{dean2008mapreduce}
and has subsequently implemented by many open source systems. Those systems
provide handy APIs with fualt tolerances and are popularly
used as large-scale data processing platforms. 
% become a ubiquitous parallel platform for large-scaled data processing. 
%Current open source MapReduce systems provide handy programming APIs with fault tolerances
%in backends. Such systems include Hadoop, Shark and Spark to name a few.
In simple words, there are two conceptual types of computing nodes in MR,
namely the \emph{mapper}s and the \emph{reducer}s. The execution of a MR 
algorithm consists of three stages: First, input data
are partitioned and read by a \emph{map} function on each mapper. Then, mappers
emit key-value pairs which are \emph{shuffle}d over the network to reducers. Finally,
reducers process received data using a \emph{reduce} function then write the
outputs.

Despite the simpleness of the paradigm, there are two concerns raised in designing MR algorithms
First, since it requires reducers to be independent, partitioning  
data to fit the independence could be challenging. Second, since the \emph{shuffle}
stage requires network access, the data been shuffled should be minimized. 
We take these concerns in consideration in designing our solutions for mining GCMP.
%We would bare this concerns in designing our GCMP mining algorithm.
%a natural
%problem is how to partition the data in map and shuffle phase so that reducers 
%achieve the independence.
%
%A critical question in designing a MapReduce algorithm is how to make 
%data partitions during the shuffle stage. In fact, a MapReduce algorithm 
%requires data processed at each reducer to be independent.
%
%Since the \emph{shuffle} stage needs to transfer data over network, 
%an important attention to pay during designing MapReduce an algorithm is 
%to minimize the shuffle amounts and shuffle counts.

\subsection{MapReduce Processing for Mining GCMP}
Our GCMP mining process consists of two MR jobs. The two jobs
contains four MR stages as illustrated in Figure~\ref{fig:overview}.
The first MR job is to cluster objects at each snapshot (i.e.,
computing $\forall t, o, C_t(o)$). As shown in Figures~\ref{fig:overview}(a)-(b),
trajectories are first reorganized by timestamps in map phase and object locations
at the same timestamps form a cluster. The clustering takes place in reduce phase, where
each snapshot is processed independently. The second MR job is to mine GCMPs from 
clusters at each snapshot. We design two MR algorithms (i.e., TRM and SPM) for 
the purpose of comparison. Both the two algorithms would partition snapshots in map phase
(as in Figure~\ref{fig:overview}(c))
and mine GCMPs from each partition in reduce phase(as in Figure~\ref{fig:overview}(d)).

% corresponds to Figures~\ref{fig:overview}(a)-(b). The objective
%of the first job is to cluster trajectories based on snapshots (i.e.,).
%As illustrated in (a), input trajectories are read in by mappers 
%and are sprinkled into $\langle t,o \rangle$ pairs. In (b), objects with the same timestamp
%form a snapshot. Then, a user defined clustering method is applied on the objects
%in each snapshot in reducers. Between step (a) and (b), a shuffle is necessary. 
%The second
%MapReduce job corresponds to Figures~\ref{fig:overview} (c)-(d). The objective 
%of the second job is to mine the GCMP from the snapshots computed in the first job. We design
%two approaches (to be described shortly)for mining GCMP in parallel. In overview, as shown in (c), snapshots
%are first fed to mappers and different partition strategies may be selected to create
%partitions among snapshots. In (d), the partitions are then send to reducers to mine GCMP.
%The final computed results are then outputted to the end users.

Although we need two MR jobs to complete the GCMP mining task, 
it is easy to pipeline the two jobs to exploit data locality.
Specifically, the reducer output at step (b) can be directly reused 
as the input to mappers at step (c). Therefore we do not need to 
transfer data from (b) to (c). Modern MR platforms, especially Spark, have
already supported such a kind of pipeline.

\begin{figure} [t]
\center
\includegraphics[width=0.5\textwidth]{system_layout.eps}
\caption{System flow of mining GCMP. (a)(b) correspond to the first MR job which compute the clusters at each snapshot; 
(c)(d) correspond to the second MR jobs which mines GCMP in parrallel.}
\label{fig:overview}
\end{figure}

We note that the first MR job is easy to design since each reducer only
needs one snapshot for clustering.
In contrast, it is challenging to design the second job. 
This is because valid patterns may spray across multiple snapshots, where inappropriate partitioning
of snapshots may fail to discover certain valid patterns.
Formally, a reasonable partition strategy 
needs to meet the following requirements: (a) the resulted partitions need
to preserve enough information so that real patterns can be discovered in the reduce phase. 
(b) the resulted partitions need to ensure that
the patterns discovered in the reduce phase are valid patterns so that
no further verification is required. We formalize the two 
properties as \emph{completeness} and \emph{soundness} as follows:

\begin{definition}[Completeness and Soundness]
Let a partition method $\mathbb{P}$ partitions original trajectories $Tr$ into multiple parts, $Par_1,...,Par_m$. $\mathbb{P}$ is complete if for every pattern $P$ that is valid in $Tr$, $\exists Par_i$ such that $P$ is valid in $Par_i$. $\mathbb{P}$ is sound if for all patterns $P$ that is valid in any $Par_i$, it is also valid in $TR$.
\end{definition}
The completeness ensures that no true patterns are missed out. 
The soundness ensures that no false patterns are reported. 
If a partition method is both sound and complete, then it can be used
in the second MR job to facilitate GCMP mining.

Apparently, replicating the entire trajectories to each 
partition meets the \emph{soundness} and \emph{completeness} requirements. 
However, it burdens the network shuffle and limits the parallelism. 
Our objective is thus to design a complete and sound partition method that minimize the network shuffles.
In the following sections, we describe a naive \emph{temporal-based} partition-and-mining method called \emph{Temporal Replication and Mining}(TRM) towards a parallel solution of GCMP mining. Then,
we present a novel \emph{object-based} partition-and-mining method
called \emph{Star Partition and Mining} (SPM) which resolves
the deficiencies of TRM method.
